Cluster Paper

### 2015-04-22 ms.tex
continue to add text

\shorttitle{Cluster Paper}
\shortauthors{BOADA ET AL.}

@@

\section{Recovery of Cluster Parameters, Full Knowledge}

@@

We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 107748 galaxies comprising 1683 unique halos, and we find a RMS$[\delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\delta z = z_{c,true} - z_{c}$.

\editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight. I don't think that will be the case when we get more complicated things.}

\subsection{Line of Sight Velocity Dispersion}
The unbiased estimation of a standard deviation (a measure of statistical dispersion) is a technically involved problem. At first, we require that our estimator be unbiased in that the dispersion estimation is equal to the true dispersion, although, in practice this rarely occurs. The most commonly used estimate is the corrected sample standard deviation, given by:
\begin{equation}
	s = \sqrt{\frac{1}{n-1} \sum_{i=1}^n (x_i - \bar{x})^2}
\end{equation}
with $\{x_1, x_2, ..., x_n\}$ is the random sample and $\bar{x}$ is the sample mean. The corrected sample standard deviation has the advantage in that it is unbiased (as opposed to the population standard deviation which is biased), but the removal of bias relies on knowing \textit{a priori} the underlying distribution from which the sample is drawn. An estimator which correctly estimates a standard deviation for a sample drawn from a wide range of distributions and is not adversely effected by outliers is said to be \textit{robust}.

A robust estimator becomes critical as it minimizes the effect that outliers which may remain after the rejection of non-cluster members have on the measured dispersion. \cite{Beers1990} present a robust estimation of scale (yet another term for statistical dispersion) called the biweight scale estimator. \cite{Ruel2014} note that the biweight scale estimator is biased and suggest a correction.

>>>>

\shorttitle{HETDEX PAPER}
\shortauthors{BOADA ET AL.}

@@

\section{Analysis}

@@

We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 107748 galaxies comprising 1683 unique halos, and we find a RMS$[\delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$. \editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight. I don't think that will be the case when we get more complicated things.}

\subsection{Line of Sight Velocity Dispersion}
We first calculate the line of sight velocity (LOSV) to each galaxy, where
\begin{equation}
	LOSV = c\frac{z - z_c}{1+z_c}
\end{equation}
and $c$ is the speed of light in \kms, $z$ is the redshift of the individual galaxy, and $z_c$ is the overall cluster redshift described in the previous section.

The unbiased estimation of a standard deviation (a measure of statistical dispersion) from these LOSVs is a technically involved problem. At first, we require that our estimator be unbiased in that the dispersion estimation is equal to the true dispersion, although, in practice this rarely occurs. The most commonly used estimate is the corrected sample standard deviation, given by:
\begin{equation}
	s = \sqrt{\frac{1}{n-1} \sum_{i=1}^n (x_i - \bar{x})^2}
\end{equation}
with $\{x_1, x_2, ..., x_n\}$ being the random sample and $\bar{x}$ the sample mean. The corrected sample standard deviation has the advantage in that it is unbiased (as opposed to the population standard deviation which is biased), but the removal of bias relies on knowing \textit{a priori} the underlying distribution from which the sample is drawn. An estimator which correctly estimates a standard deviation for a sample drawn from a wide range of distributions and is not adversely effected by outliers is said to be robust.

In our situation, a robust estimator becomes critical as it minimizes the effect of outliers which the inclusion of non-cluster members have on the measured dispersion. \cite{Beers1990} present a robust estimation of scale (yet another term for statistical dispersion) called the biweight scale estimator. \cite{Ruel2014} note, however, that the biweight scale estimator is biased and suggest a correction.
